

```{r}
library(ERBS)
data(HepG2)
data(GM12878)
res = findOverlaps(HepG2,GM12878)
erbs = HepG2[queryHits(res)]


```
Indexing individual ranges
Where does the 17th HepG2 region start?

```{r}
HepG2[17,]
```


```{r}
x<-distanceToNearest(GM12878,HepG2[17,])

x          

```

```{r}

min()

m<-which(mcols(x)$distance==min(mcols(x)$distance))
```


#Hassan bht achay  ho Ap
```{r}
GM12878[queryHits(x[m,]),]
```

Q3: Measuring distance between closest regions
1/1 point (graded)
What is the distance between the 17th region of HepG2 and its closest region in GM12878?




```{r}

min(mcols(x)$distance)
```


Q4: Summarizing proximities of nearest regions in a pair of GRanges
1 point possible (graded)
For each region in HepG2 find the closest region in GM12878 and record the distance.

What proportion of these distances are smaller than 2000 base pairs?
Distance is a metadata column on the Hits object, so consider using mcols().
```{r}
length(HepG2)
```


```{r}
st<-0

for(i in 1:length(HepG2)){
  x<-distanceToNearest(HepG2[i,],GM12878)
  
    st[i]<-min(mcols(x)$distance)
}
sum(st<2000)/length(st)
```

another
```{r}
d = distanceToNearest(HepG2,GM12878)
mean(mcols(d)$distance < 2000)
```





```{r}
order(erbs)
```



```{r}
erbs = granges(erbs)
erbs[order(erbs),]

```

```{r}
erbs2= intersect(HepG2,GM12878)
erbs2[order(erbs2),]

```

