## before video, run code from previous video AND these commands:


```{r}
res = findOverlaps(HepG2,GM12878)
erbs = HepG2[queryHits(res)]
erbs = granges(erbs)

```

# define human genes

```{r}
library(Homo.sapiens)
ghs = genes(Homo.sapiens)
ghs

```

# learn about the precede function (and related functions like follow)

```{r}
?precede

```

# for each range in erbs, find the closest preceding range in ghs

329145 is closest and preceds 361308

20335787 is closest and preceds 20251789 (-negative)
```{r}
index = precede(erbs, ghs)
ghs[index[1:3]]
erbs[1:3]    # note result is strand-aware

```




Now, if we want to compute the distance between each binding
site and its corresponding gene found with precede,
```{r}
ds = distance(erbs, ghs[index])
```

we're going to find the transcription start site that's closest.




```{r}
tssgr = resize(ghs, 1)
tssgr
```
and what we want to do now is for each of our binding sites,
we want to find the closest transcription start site,
and there's a function that does that-- I think we saw it earlier--
called distanceToNearest.


```{r}
d = distanceToNearest(erbs, tssgr)
queryHits(d)


dists = values(d)$distance



```

So now we see that many of our sites of interest--
let's constrain the range a little bit-- are very close.
A lot of them are very close to the transcription start sites.
We consider that to be good news because now we
can make more sense of the biology for binding sites
that are very close to our transcription start sites.
So that is be a nice result that we just found, and now another thing we can do


```{r}
hist(dists, nc=100, xlim=c(0,100000))

```




is we can take a closer look at the genes that are
close to our transcription start sites.
How do we do that?
First, let's get the index of the genes that are closest.
I'm going to do this, subjectHits d.
That's my index.
But now, I want the ones that are closer than,
let's say, 1,000, so very close to our binding sites, say less than 1,000.

```{r}
index = subjectHits(d)[dists < 1000]
index
```




