


```{r}
library(Homo.sapiens)
ghs = genes(Homo.sapiens)
```
and what you learned in the video, convert the ghs object to one that represents just the tss

What is the TSS (Transcription Start Site) of the gene with ID: 100113402?
Hint: look at the ghs in the console. Note that the names of the ranges are the same as the GENEID column, so you can index the ranges directly with "100113402".

```{r}
tss <- resize(ghs,1)
start(tss["100113402"])
```
What is the GENEID of the gene with TSS closest to the 4th region of erbs?
Hint: Use the nearest() function.

```{r}

library(ERBS)
data(HepG2)
data(GM12878)
res = findOverlaps(HepG2,GM12878)
erbs = HepG2[queryHits(res)]
erbs = granges(erbs)
distanceToNearest(erbs[4,], tss)

values(tss[6316,])$GENEID

keytypes(Homo.sapiens)
keys = as.character(values(tss[6316,])$GENEID)
columns(Homo.sapiens)
res = select(Homo.sapiens, keys = keys,
             columns = c("SYMBOL", "ENTREZID"), keytype="GENEID")
res

```





```{r}
library(Homo.sapiens)
ghs = genes(Homo.sapiens)
tssgr= resize(ghs,1)
i = nearest(erbs[4],tssgr)
gene<-as.character(values(tssgr[i])$GENEID)
res=select(Homo.sapiens,key=gene,keytype="GENEID",column="SYMBOL")
res
```

