```{r,eval=FALSE}

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("airway")
```


```{r}
library(airway)
```

```{r}

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(c("Homo.sapiens"))
```
```{r}
library(Homo.sapiens)
class(Homo.sapiens)
```
```{r}
methods(class=class(Homo.sapiens))
```
## Installing Bioconductor
In order to install Bioconductor, copy the following two lines into your R console.
This will install the core Bioconductor packages. Further packages can be installed using the biocLite function and specifying a character vector of which packages to install. For example, to install the “affy” and “genefilter” libraries you would type:

```{r}

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(c("genefilter","geneplotter"))
```
```{r}
library(genefilter)
```

```{r}
help.start()
```

http://genomicsclass.github.io/book/pages/installing_Bioconductor_finding_help.html

# Help Function

```{r}
?mean
```


```{r}
example(mad)
```

```{r}
help(package="genefilter", help_type="html")

```



```{r}
library(geneplotter)
```

```{r}
#geneplotter::
```


```{r}
class(6)
?numeric
?"numeric-class"

```



```{r}
library(Biobase)
```



```{r}
?ExpressionSet
?"ExpressionSet-class"
```



```{r}
methods(class="ExpressionSet")
methods(class="lm")

```



```{r}
data(sample.ExpressionSet)
methods(class=class(sample.ExpressionSet))
```

```{r}
vignette(package="Biobase")
```

```{r}
vignette("ExpressionSetIntroduction")

```

```{r}
browseVignettes(package="Biobase")
```

