```{r}
BiocManager::install(c("Biobase",
                       "GEOquery",
                       "genomicsclass/GSE5859Subset",
                       "affy",
                       "hgu95acdf",
                       "genefilter",
                       "parathyroidSE",
                       "airway",
                       "pasillaBamSubset",
                       "Rsamtools",
                       "GenomicAlignments",
                       "ArrayExpress",
                       "NGScopyData",
                       "TxDb.Hsapiens.UCSC.hg19",
                       "AnnotationDBI"))


```

matrix contains microarray values stored in exprs

```{r}
#1st sample

exprs(e)[1,]

#1st feature

exprs(e)[,1]




```

rownames are probsets

```{r}
rownames(e)
```

use the pData function
and this gives us a data frame, which is information
about the columns of the ExpressionSet.

```{r}

```

The feature data is accessible with fData function
and this is information about the rows, which are genes or probe sets.



```{r}

```

are the, for example, the gene title or the gene symbol
or the ENTREZ gene ID or Gene Ontology information, which
might be useful for downstream analysis.
And so you can access these with the dollar sign
and you can see that there's 4,000 different gene
symbols represented in these 9,000 rows.
So it looks like there's some duplication of gene symbols.

```{r}
head(fData(e)$"Gene Symbol")
head(rownames(e))
```

```{r}
library(Biobase)
library(GEOquery)

geoq <- getGEO("GSE9514")    # download a microarray dataset from GEO
names(geoq)    
e <- geoq[[1]]    # extract ExpressionSet
e

# exprs gives matrix of microarray values
dim(e)    # number of features and samples in ExpressionSet
ncol(e)
nrow(e)

exprs(e)[1:3,1:3]
head(exprs(e))[,1]    # first column
exprs(e)[1,]    # first row
exprs(e)["10000_at",]    # can also index by name
rownames(e)[1]    # row names are probe sets
dim(exprs(e))    # rows are features, columns are samples

# pData gives phenotype data (sample information)
pData(e)[1:3,1:6]
names(pData(e))
pData(e)$characteristics_ch1    # column in GEO to describe experimental state/condition
as.numeric(pData(e)$characteristics_ch1)    # help see replicates of each state
dim(pData(e))    # rows of pData correspond to columns of exprs
dim(e)

# fData gives feature data (probe information)
fData(e)[1:3,1:3]
dim(fData(e))    # rows of fData correspond to rows of exprs
names(fData(e))
head(fData(e)$"Gene Symbol")
head(rownames(e))

# additional annotation tied to ExpressionSet
experimentData(e)
```

