Explore a SummarizedExperiment object and practice accessing and manipulating data from various components of the object. To complete this assessment, install and load the airway package. This package contains a SummarizedExperiment object called airway containing RNA-seq data from untreated and steroid-treated airway smooth muscle cell lines.


```{r}
library(airway)
data(airway)
airway    # SummarizedExperiment object


```


Q1: Metadata
0.0/1.0 point (graded)
Inspect the metadata for the airway dataset.
```{r}
metadata(airway)
```

What is the PubMed ID (PMID) for the original paper supplying these data?

```{r}
24926665
```



Some problems have options such as save, reset, hints, or show answer. These options follow the Submit button.

Save Save Your Answer
Q2: Number of features and samples
0.0/2.0 points (graded)
Inspect the dimensions of the airway dataset.


```{r}
dim(airway)
```

How many features are in the dataset?
  unanswered 
```{r}
length(rowRanges(airway))
```

How many samples are in the dataset?


```{r}
length(colData(airway))
```


Save Save Your Answer
Q3: Sample data
0.0/3.0 points (graded)
Explore the sample metadata for the airway dataset. The columns of the metadata table are given informative abbreviated names, but their exact meaning needs to be inferred.
```{r}
names(colData(airway))
```
```{r}
which(colnames(airway)=="SRR1039509")
```


Which cell line is associated with sample SRR1039509?

```{r}

colData(airway)[which(airway$Run=="SRR1039509"),]$cell


```


What is the name of the metadata column specifying whether the sample was treated with dexamethasone (a steroid)?

```{r}
colData(airway)[which((colData(airway))$avgLength==min(colData(airway)$avgLength)),]

```

Which sample (column name) has the shortest average read length?
  
```{r}
 min((colData(airway))$avgLength)

```

Q4: Feature data

Explore the feature metadata for the airway dataset.



Each feature (row) in the dataset corresponds to a single gene. How many genes are in the dataset?

```{r}
length(rowRanges(airway))
```


 
The row metadata for the airway object include GRanges specifying the exon boundaries for each gene. How many exons are in the 100th gene?
  unanswered 
```{r}

length(rowRanges(airway)[[100]])

```


Save Save Your Answer
Q5: Exploring a particular feature with GRanges
0.0/3.0 points (graded)
Use GRanges operations to explore properties of the 100th gene in the dataset.
```{r}
sum(width(ranges(rowRanges(airway)[[100]])))
```

On which chromosome is the 100th gene?
  unanswered 
```{r}
7
```


```{r}
ir<-rowRanges(airway)[100]
```


```{r}
width(range(rowRanges(airway)[[100]]))

```


How many bases long is the 100th gene (including introns)?
exclude overlapping ranges the calculate width Nice..
```{r}
intersect(ranges(ir))
```

```{r}
ir[ir %over% ir]
```


```{r}


```


```{r}
sum(seqlengths(rowRanges(airway)[[100]]))
```
```{r}
sum(width(reduce(ranges(ir))))

```

```{r}

width(range(reduce(ranges(ir))))
```


TRUE including introns

```{r}
width(range(rowRanges(airway)[[100]]))
```


What is the transcription start site (TSS) of the 100th gene?

```{r}
ir2 <- sort(ranges(ir))
ir2


```

```{r}
start(resize(ir2,1))[[1]]
```


```{r}
```

```{r}
resize(range(rowRanges(airway)[[100]]), 1)

```


Save Save Your Answer
Q6: Assay information for a specific feature
0.0/4.0 points (graded)
Consider the gene with ENSEMBL ID "ENSG00000103196".
```{r}
mean(assay(airway)[(rownames(assay(airway))=="ENSG00000103196")])
```


What is the mean expression level of this gene across all samples?

```{r}
mean(assay(airway)[(rownames(assay(airway))=="ENSG00000103196")])

```

What is the mean expression level of this gene in samples treated with dexamethasone?
Use which() on the sample information table to identfy which samples have the dexamethasone status "trt".


```{r}
head(assay(airway))
```

```{r}
```

```{r}
x<-sum(assay(airway[,which(colData(airway)$dex=="trt")]))
```


```{r}
y<-ncol(assay(airway[,which(colData(airway)$dex=="trt")]))*nrow(assay(airway[,which(colData(airway)$dex=="trt")]))
```

```{r}
x/y
```

```{r}

head(assay(airway))
```


```{r}
colData(airway)
```





```{r}
colData(airway)
```
```{r}
head(assay(airway)[1,])
```


What is the mean expression level of this gene in untreated control samples?
Use which() on the sample information table to identfy which samples have the dexamethasone status "untrt".

```{r}
sum(colSums(assay(airway[,which(colData(airway)$dex=="trt")])))/y

```

What is the log (base 2) ratio of mean expression of this gene between treated and untreated samples?
  unanswered 
  
```{r}
log2(335.2284/349.2917)
```

