In the video we talk about phenotypes. Here we show some examples of what we mean by phenotypes, how they can be coded in R objects, and how we compute with them. Later in the course we will perform analyses that statistically  connect these phenotypes to measured molecular outcomes. Here we explore the use of data frames to store phenoypes (columns) from several individuals (rows).

# Tabulating gender representation

Install and attach the COPDSexualDimorphism.data package using biocLite. Use the commands
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("COPDSexualDimorphism.data")
```
```{r}
library(COPDSexualDimorphism.data)
data(lgrc.expr.meta)

```

Install and attach the COPDSexualDimorphism.data package using biocLite. Use the commands

library(COPDSexualDimorphism.data)
data(lgrc.expr.meta)
to add the object expr.meta to your workspace. The variable pkyrs in the expr.meta data.frame represents pack years smoked. Other variables include gender (self-explanatory) and diagmaj (disease status).

What is the number of female participants in this study?:

```{r}
sum(expr.meta$GENDER=='2-Female')
```

What is the median of the distribution of pack years smoked in this cohort (women and men)?

```{r}
median(expr.meta$pkyrs)
```


True or False: The distribution of pack-years smoked is well-approximated by a Gaussian (Normal) probability distribution.

Select one:
```{r}


hist(expr.meta$pkyrs)
qqnorm(expr.meta$pkyrs)
qqline(expr.meta$pkyrs)

```
Exploratory comparison of distributions
The units with which a quantity is recorded are not always the most effective for statistical analysis.

Use the command boxplot(pkyrs~gender, data=expr.meta) to examine the distributions of pack years by gender using the boxplot statistics and outlier flagging.

Which of the following is an aspect of the display that would suggest caution in using the t test in comparing males and females with respect to pack years smoked?

```{r}
boxplot(pkyrs~gender, data=expr.meta)
```
## Variable transformation
1 point possible (graded)
Use the code expr.meta$pyp1 = expr.meta$pkyrs+1 to define a positive-valued variable for transformation analysis.

Then load the MASS package (library(MASS)) and fit the model lm1 = lm(pyp1~gender, data=expr.meta) that tests for a difference in mean pack years (plus 1) between genders.

Finally, use boxcox(lm1) to see a plot of the likelihood function for a transformation model. Under this model we use a number denoted lambda that for our purposes is used as an exponent to transform the dependent variable pyp1 of the regression to have a distribution that is approximately Gaussian. Thus, if lambda is 1, we use pyp1 untransformed, if lambda is 0.5, we use sqrt(pyp1), and so on.

For what value of lambda does the likelihood reach its highest value for the model lm1?

```{r}
expr.meta$pyp1 = expr.meta$pkyrs+1
```


```{r}
library(MASS)
```



```{r}
lm1 = lm(pyp1~gender, data=expr.meta)
```


```{r}
boxcox(lm1)
```
Once you have read the plot to obtain the value of lambda at which the transformation model likelihood is maximized, use the code boxplot(I(pyp1^lambda)~gender, data=expr.meta) to see the effects of the transformation on symmetry and presence of outliers.

Transformations with similar intent will be important in various aspects of statistical analysis of genome-scale data.
```{r}
lambda <- 0.5
boxplot(I(pyp1^lambda)~gender, data=expr.meta)
```

