```{r}
library(tissuesGeneExpression)
data(tissuesGeneExpression)
library(SummarizedExperiment)
tissSE = SummarizedExperiment(list(rma=e))
colData(tissSE) = DataFrame(tab)
library(hgu133a.db)
sym = mapIds(hgu133a.db, keys=rownames(tissSE), column="SYMBOL", keytype="PROBEID")
nm = mapIds(hgu133a.db, keys=rownames(tissSE), column="GENENAME", keytype="PROBEID")
rowData(tissSE) = DataFrame(symbol=sym, genename=nm) 
```



```{r}
grep("H2AFX", rowData(tissSE)$symbol, value=TRUE)

```

```{r}
sum((grep("^H2A", rowData(tissSE)$symbol, value=TRUE)))
```
Verify that 205436_s_at is the affymetrix code for H2AFX and then consider the following pl
```{r}

assay(tissSE["205436_s_at",])

```

```{r}
par(las=2, mar=c(10,4,2,2))
boxplot(as.numeric(assay(tissSE["205436_s_at",]))~tissSE$Tissue)
```





```{r}
par(las=2, mar=c(10,4,2,2))
boxplot(as.numeric(assay(tissSE["205436_s_at",]))~tissSE$Tissue)
```
grepl & grep
In their most basic form, regular expressions can be used to see whether a pattern exists inside a character string or a vector of character strings. For this purpose, you can use:

grepl(), which returns TRUE when a pattern is found in the corresponding character string.
grep(), which returns a vector of indices of the character strings that contains the pattern.
Both functions need a pattern and an x argument, where pattern is the regular expression you want to match for, and the x argument is the character vector from which matches should be sought.

In this and the following exercises, you'll be querying and manipulating a character vector of email addresses! The vector emails has already been defined in the editor on the right so you can begin with the instructions straight away!
```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use grepl() to match for "edu"

grepl('edu',emails)
# Use grep() to match for "edu", save result to hits

hits<-grep('edu',emails)
hits
# Subset emails using hits
emails[hits]

```

grepl & grep (2)
You can use the caret, ^, and the dollar sign, $ to match the content located in the start and end of a string, respectively. This could take us one step closer to a correct pattern for matching only the ".edu" email addresses from our list of emails. But there's more that can be added to make the pattern more robust:

@, because a valid email must contain an at-sign.
.*, which matches any character (.) zero or more times (*). Both the dot and the asterisk are metacharacters. You can use them to match any character between the at-sign and the ".edu" portion of an email address.
\\.edu$, to match the ".edu" part of the email at the end of the string. The \\ part escapes the dot: it tells R that you want to use the . as an actual character
```{r}

grep("GAPDH", rowData(tissSE)$symbol, value=TRUE)
 sum(rowData(tissSE)$symbol=='H2AFX',na.rm=TRUE)
```





